Irt plot extra

### 2022-02-16 appendix-1.Rmd
Typo corrected

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
```

@@

```{r sixFacTab}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
```

@@

```{r EFAsix}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
```

@@

```{r unmerged-data, include =F}
unmerged <- read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
```

```{r unmertab}
apa_table(unmerged , longtable =T, font_size = "footnotesize")
```

```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve ', out.width='100%'}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```

```{r F1IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', include=FALSE, out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
```

```{r F2IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2. All items cariied information across the latent trait continuum. Item 09 carried the lowest information however its information peak was highr than .20.', include=FALSE, out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
```

```{r F3IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3. Item 30 and 41 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
```

```{r F4IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
```

```{r F5IF, eval=FALSE, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5. Three items: 25, 04, 01 carriedlow information. However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.  Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 600)
```

>>>>

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minimum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
```

@@

```{r sixFacTab}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items (six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
```

@@

```{r EFAsix}
apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
```

@@

```{r unmerged-data, include =F}
unmerged <- readxl::read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
```

```{r unmertab}
apa_table(unmerged , longtable =T, font_size = "footnotesize", caption = "Five factor obtained from the unmerged data.")
```

```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30, & 41) had relatively flat information curves ', out.width='100%', out.height='80%'}
knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
```
